


\Large\textbf{References}\normalsize


[1]	Gabriel Bracha. Asynchronous byzantine agreement protocols. Information and Computation, 75(2):130–143, 1987.

[2]	Ethan Buchman, Jae Kwon, and Zarko Milosevic. The latest gossip on BFT consensus. http:// arxiv.org/abs/1807.04938v2, 2018.

[3]	Michael Burrows. The chubby lock service for loosely-coupled distributed systems. In 7th Symposium on Operating Systems Design and Implementation (OSDI ’06), November 6-8, Seattle, WA, USA, pages 335–350, 2006.

[4]	Vitalik Buterin and Virgil Griffith. Casper, the friendly finality gadget. https://arxiv.org/abs/ 1710.09437, 2017.

[5]	Apache	Cassandra.	Apache	cassandra.	Website, http://planetcassandra.org/ what-is-apache-cassandra.

[6]	Miguel Castro and Barbara Liskov. Practical byzantine fault tolerance. In 3rd symposium on Operating Systems Design and Implementation (OSDI’99), volume 99, pages 173–186, 1999.

[7]	TH Hubert Chan, Rafael Pass, and Elaine Shi. Pala: A simple partially synchronous blockchain. https://eprint.iacr.org/2018/981, 2018.

[8]	James C. Corbett, Jeffrey Dean, Michael Epstein, Andrew Fikes, Christopher Frost, J. J. Furman,
Sanjay Ghemawat, Andrey Gubarev, Christopher Heiser, Peter Hochschild, Wilson C. Hsieh, Sebastian Kanthak, Eugene Kogan, Hongyi Li, Alexander Lloyd, Sergey Melnik, David Mwaura, David Nagle, Sean Quinlan, Rajesh Rao, Lindsay Rolig, Yasushi Saito, Michal Szymaniak, Christopher Taylor, Ruth Wang, and Dale Woodford. Spanner: Google’s globally distributed database. ACM Trans. Comput. Syst., 31(3):8:1–8:22, 2013.

[9]	Cynthia Dwork, Nancy Lynch, and Larry Stockmeyer. Consensus in the presence of partial synchrony. Journal of the ACM (JACM), 35(2):288–323, 1988.

[10]	etcd community. etcd. Website, https://etcd.io/.

[11]	Rati Gelashvili, Lefteris Kokoris-Kogias, Alberto Sonnino, Alexander Spiegelman, and Zhuolun Xiang. Jolteon and ditto: Network-adaptive efficient consensus with asynchronous fallback. arXiv preprint arXiv:2106.10362, 2021.

[12]	Guy Golan Gueta, Ittai Abraham, Shelly Grossman, Dahlia Malkhi, Benny Pinkas, Michael K Reiter, Dragos-Adrian Seredinschi, Orr Tamir, and Alin Tomescu. SBFT: a scalable decentralized trust infrastructure for blockchains. In DSN, 2019.

[13]	Patrick Hunt, Mahadev Konar, Flavio Paiva Junqueira, and Benjamin Reed. Zookeeper: Wait-free coordination for internet-scale systems. In 2010 USENIX Annual Technical Conference, Boston, MA, USA, June 23-25, 2010, 2010.

[14]	Eleftherios Kokoris Kogias, Philipp Jovanovic, Nicolas Gailly, Ismail Khoffi, Linus Gasser, and Bryan Ford. Enhancing bitcoin security and performance with strong consistency via collective signing. In 25th {usenix} security symposium ({usenix} security 16), pages 279–296, 2016.

[15]	Leslie Lamport, Robert Shostak, and Marshall Pease. The byzantine generals problem. ACM Transactions on Programming Languages and Systems (TOPLAS), 4(3):382–401, 1982.

[16]	Satoshi Nakamoto. Bitcoin: A peer-to-peer electronic cash system. http://bitcoin.org/bitcoin. pdf, 2008.

[17]	Maofan Yin, Dahlia Malkhi, Michael K. Reiter, Guy Golan Gueta, and Ittai Abraham. Hotstuff: BFT consensus with linearity and responsiveness. In 38th ACM symposium on Principles of Distributed Computing (PODC’19), 2019.